---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures"
)
```

# R package `SBLF`

`r badger::badge_devel("umich-biostatistics/SBLF", "blue")` `r badger::badge_code_size("umich-biostatistics/SBLF")`

## Overview

This `R` package provides a user-friendly interface for fitting spatial Bayesian latent factor models. Uncover the latent brain image structure using image on image regression.

## Installation

The package is currently only runnable on Linux. Windows or Mac users can run a virtual Linux distribution on their machine or use a cluster.  

To install, open `R` and run:

If the devtools package is not yet installed, install it first:
```{r, eval=FALSE}
install.packages('devtools')
library(devtools)
```

```{r, eval = FALSE}
# install SBLF from Github:
install_github('umich-biostatistics/SBLF') 
library(SBLF)
```

## Example usage

### Quick example: 

```{r, eval = FALSE}
?SBLF
mod = SBLF(xtrain, xtest, ztrain, ztest, voxel_loc, seed = 1234, burnin = 250, iter = 500)
```
